extractr
=======

```{r echo=FALSE}
library("knitr")
hook_output <- knitr::knit_hooks$get("output")
knitr::knit_hooks$set(output = function(x, options) {
   lines <- options$output.lines
   if (is.null(lines)) {
     return(hook_output(x, options))  # pass to default hook
   }
   x <- unlist(strsplit(x, "\n"))
   more <- "..."
   if (length(lines)==1) {        # first n lines
     if (length(x) > lines) {
       # truncate the output, but add ....
       x <- c(head(x, lines), more)
     }
   } else {
     x <- c(if (abs(lines[1])>1) more else NULL,
            x[lines],
            if (length(x)>lines[abs(length(lines))]) more else NULL
           )
   }
   # paste these lines together
   x <- paste(c(x, ""), collapse = "\n")
   hook_output(x, options)
 })

knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  warning = FALSE,
  message = FALSE
)
```

`extractr` is an R package with interfaces to various extraction services, from web APIs and from local software, including:

* [XPDF](http://www.foolabs.com/xpdf/)
* [Ghostscript](http://www.ghostscript.com/)
* [Rcampdf](http://datacube.wu.ac.at/)
* [pdfx](http://pdfx.cs.man.ac.uk/usage)
* [Poppler](http://poppler.freedesktop.org/)
* more to come ...

## Installation

For now, you'll need one pkg that's not on CRAN. May remove this dependency in the future. 

```{r eval=FALSE}
install.packages("Rcampdf", repos = "http://datacube.wu.ac.at/", type = "source")
```

Install `extractr`

```{r install, eval=FALSE}
install.packages("devtools")
devtools::install_github("sckott/extractr")
```

Load the package

```{r}
library("extractr")
```

## extract with local utilties

Get path to an example pdf, comes with the package

```{r}
path <- system.file("examples", "example1.pdf", package = "extractr")
```

### xpdf

xpdf is the default. The structure of the three method options (`xpdf`, `gs`, `rcamp`) for extracting using the `extract()` function give the same structure back: a simple list, a slot for metadata attached to the PDF, and a slot for data (the extracted text).

```{r output.lines = 1:15}
xpdf <- extract(path, "xpdf")
xpdf$meta
```

Since the character string is very long, we'll just print a few hundred characters to give you a flavor of the text

```{r}
substr(xpdf$data, 1, 200)
```

### gs - Ghostscript

```{r output.lines = 1:15}
gs <- extract(path, "gs")
gs$meta
```

```{r}
substr(gs$data, 1, 200)
```

### rcamp - Rcampdf

```{r output.lines = 1:15}
rcamp <- extract(path, "rcamp")
rcamp$meta
```

```{r}
substr(rcamp$data, 1, 200)
```

### poppler - Rpoppler

```{r output.lines = 1:10}
poppler <- extract(path, "poppler")
poppler$meta
```

```{r}
substr(poppler$data, 1, 200)
```

## pdfx - A web API

```{r pdfx, eval=FALSE}
path <- system.file("examples", "example1.pdf", package = "extractr")
res <- pdfx(file = path)
```

The metadata

```{r output.lines = 1:10, eval=FALSE}
res$meta
```

The extracted text

```{r output.lines = 1:15, eval=FALSE}
res$data   
```


## Meta

> NOTE: Some of the code in this package has been adapted from the `tm` R package (`GPL-3` licensed), where we've borrowed some of their code for extracting text from PDFs, but have modified the code. 
